Cooperative Kernels: GPU Multitasking for Blocking Algorithms

### 2017-07-06 write-ups/FSE/paper.tex
added a note about special hardware support being required for preemption

\newcommand{\ADComment}[1]{\textcolor{green}{AD: #1}}
%\newcommand{\TSComment}[1]{\textcolor{blue}{TS: #1}}
\newcommand{\TSAdded}[1]{\textcolor{blue}{#1}}
\newcommand{\TSEmph}[1]{\textcolor{red}{#1}}
\newcommand{\HEComment}[1]{\textcolor{orange}{HE: #1}}
%\newcommand{\COULDCUT}[1]{\textcolor{blue}{#1}}
\newcommand{\TSComment}[1]{\textcolor{purple}{TS: #1}}

@@

Suppose a graphics workload is required to be scheduled with period
$P$ and duration $D$, and that a compute kernel requires time $C$ to
execute without interruption.  If we assume the cost of preemption is
negligible (e.g.\ Nvidia have reported preemption times of 0.1 $\mathit{ms}$ for
Pascal~\cite{anandtech}), then the overhead associated with switching
between compute and graphics every $P$ time steps is $P/(P-D)$.

@@

Our low performance for heavy workloads is because the graphics task
requires half of the workgroups, crippling the cooperative kernel
enough that $\offerfork$ calls are not issued as frequently.  Future
work may examine how to insert more resizing calls in these
applications to decrease this overhead.
%
These results suggest that a hybrid preemption scheme may work
well. That is, the cooperative approach works well for light and
medium tasks; on the other hand, heavy graphics tasks benefit from the
coarser grained, kernel-level preemption strategy.

>>>>

\newcommand{\ADComment}[1]{\textcolor{green}{AD: #1}}
%\newcommand{\TSComment}[1]{\textcolor{blue}{TS: #1}}
\newcommand{\TSAdded}[1]{#1}
\newcommand{\TSEmph}[1]{\textcolor{red}{#1}}
\newcommand{\HEComment}[1]{\textcolor{orange}{HE: #1}}
%\newcommand{\COULDCUT}[1]{\textcolor{blue}{#1}}
\newcommand{\TSComment}[1]{\textcolor{purple}{TS: #1}}

@@

Suppose a graphics workload is required to be scheduled with period
$P$ and duration $D$, and that a compute kernel requires time $C$ to
execute without interruption.  If we assume the cost of preemption is
negligible (e.g.\ Nvidia have reported preemption times of 0.1
$\mathit{ms}$ for Pascal~\cite{anandtech}, because of
special hardware support), then the overhead associated with switching
between compute and graphics every $P$ time steps is $P/(P-D)$.

@@

Our low performance for heavy workloads is because the graphics task
requires half of the workgroups, crippling the cooperative kernel
enough that $\offerfork$ calls are not issued as frequently.  Future
work may examine how to insert more resizing calls in these
applications to address this.
%
These results suggest that a hybrid preemption scheme may work
well. That is, the cooperative approach works well for light and
medium tasks; on the other hand, heavy graphics tasks benefit from the
coarser grained, kernel-level preemption strategy. However, the
preemption strategy requires specialised hardware support
in order to be efficient.
